---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# writeMDX :japanese_ogre:

`writeMDX` writes Rmarkdown (`.Rmd`) files to [MDX](https://github.com/mdx-js/mdx). Nice and simple :sunglasses:

## Install :open_hands:

You can install it with `remotes::install_github("RobertMyles/writeMDX")`.

## Use :point_down:

With a file named "heyho.Rmd":

```{r eval=FALSE}
writeMDX("heyho.Rmd")
```

If you'd like to use it from the command line, first run `writeMDX::cli()`. Then it's just:

```{bash eval = FALSE}
writeMDX "heyho.Rmd"
```


## Why?? :confused:

I love [React](https://reactjs.org/), and I just rebuilt my [website](https://www.robertmylesmcdonnell.com/) using [gatsby.js](https://www.gatsbyjs.org/), so now I want all the ease and power of MDX. The only missing piece of the puzzle was doing some stuff in R, and then writing it out to an `.mdx` file that I can use to add in all the other stuff I want, like D3 graphs. R + React + Markdown = :purple_heart: 

## No CRAN? :cry:

This won't go on CRAN, since it's mainly [rmarkdown package](https://rmarkdown.rstudio.com/) functions with an added format, which you can do yourself [quite easily](https://bookdown.org/yihui/rmarkdown/format-custom.html).
